---
title: "p8105_hw1_lt2949"
output: github_document
date: "2023-09-20"
---

```{r}
library(moderndive)
library(tidyverse)

#Import date
data("early_january_weather")
early_january_weather

str(early_january_weather)
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather$temp)

#Create a scatter plot for data
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)

```
The dataset consists of 358 observations spread across 15 columns, with an average temperature of 39.58 degree Farenheit. Among these 15 attributes, we have "temp" indicating the temperature in degrees Fahrenheit at the corresponding hour. "humid" provides the humidity level for that hour. "time_hour" denotes the exact hour of the observation, and "Wind_speed" specifies the wind speed at that particular hour.


```{r}
#Pick number randomly from the normal distribution
numeric <- rnorm(10)

#Create a data frame
df <- data.frame(
  numeric,
  log_vector = numeric > 0,
  char_vector = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  fact_vector = factor(rep(1:3, length.out = 10))
)
print(df)

#Calculate means with "pull" function
mean_numeric <- mean(pull(df, numeric))
mean_numeric
mean_log <- mean(pull(df, log_vector))
mean_log

#Convert means to numeric values
x = as.numeric(mean_numeric)
x
y = as.numeric(mean_log)
y
```

